Analysis of NLA17 Dissolved Gas Indicator

### 2025-03-03 scripts/dgIndicatorAnalysis.Rmd
Updated uncertainty calculations for dissolved N2O
Updates to dgindicatorAnalysis

---
title: "Analysis of NLA17 Dissolved Gas Indicator"
authors: "J. Beaulieu, R. Martin, and M. McManus"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    fig_caption: yes
    depth: 2
    number_sections: true
    code_folding:  hide
editor_options: 
  chunk_output_type: console
---

```{r results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps
library(tictoc)
library(spmodel) # esv function

# Identify local path for each user
localPath <- Sys.getenv("USERPROFILE")

@@

```{r}
# Load data
 load(paste0(localPath,
            "/Environmental Protection Agency (EPA)/",
            "ORD NLA17 Dissolved Gas - Documents/",
            "inputData/dg.2021-02-01.RData"))

@@

```{r}
# These are the main response variables.
dg %>% 
  select(dissolved.co2.umol, dissolved.ch4.umol, dissolved.n2o.nmol, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio) %>%
  {summary(.)}

@@

```{r, fig.cap= "Fig. caption: Mean +/- 95% CI for the dissolved gas concentration indicator"}
# Read population estimates calculated with local neighborhood variance estimate.  Code provided by Tom Kincaid 
# (12/12/2019), then modified to accomdate the gas emission rate and flux variables.  See CDF_Estimates_Jb.Rmd.
pop <- read.csv(file = paste0(localPath, 
                              "/Environmental Protection Agency (EPA)/",
                              "ORD NLA17 Dissolved Gas - Documents/",
                              "inputData/populationEstimates/",
                              "NLA_2017_Percentile_Estimates_Local_Mean_JB20201202.csv"),
                as.is = TRUE) %>%
  toEPA()  # enforce formatting convention

>>>>

---
title: "Analysis of NLA17 Dissolved Gas Indicator"
authors: "J. Beaulieu, R. Martin, and M. McManus"
date: "`r Sys.Date()`"
output:
  github_document:
    number_sections: TRUE
    df_print: "tibble"
    math_method: 
      engine: webtex
    #  url: https://latex.codecogs.com/svg.image?
    html_preview: TRUE
    keep_html: TRUE
editor_options:
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

```{r setup, results='hide', message=FALSE, warning=FALSE}
# load libraries
library(sf) # spatial data
library(gstat) # lagged scatterplot, variogram
library(tidyverse) # dplyr, ggplot
library(janitor) # clean names
library(spdep) # k-NN and Moran plot
library(ncf) # ncf::correlogram
library(lattice) # xyplot
library(micromap) # linked micromaps
library(tictoc)
library(spmodel) # esv function

# Identify local path for each user
#localPath <- Sys.getenv("USERPROFILE")

@@

```{r load_data}
# Load data
load(file = "../inputData/dg.RData")
```

## Analytical uncertainty

@@

```{r responses}
# These are the main response variables.
dg %>% 
  select(dissolved.co2.umol, dissolved.ch4.umol, dissolved.n2o.nmol, co2.sat.ratio, ch4.sat.ratio, n2o.sat.ratio) %>%
  {summary(.)}

@@

```{r, fig.cap= "Fig. caption: Mean +/- 95% CI for the dissolved gas concentration indicator"}
# Read population estimates calculated with local neighborhood variance estimate.  Code provided by Tom Kincaid 
# (12/12/2019), then modified to accomdate the gas emission rate and flux variables.  See CDF_Estimates_Jb.Rmd.
pop <- read.csv(file = "../inputData/populationEstimates/NLA_2017_Percentile_Estimates_Local_Mean_JB20201202.csv",
                as.is = TRUE) %>%
  toEPA()  # enforce formatting convention
